Synpotic Soil Characterization

### 2022-10-25 3-reports/characterization_report.Rmd
loss on ignition
ICP data
update

---
title: "Untitled"
output: 
  github_document:
  html_preview: true

@@

@@

@@

@@

```{r tctnts}
tar_read(gg_tctnts)
```

@@

@@

>>>>

---
title: "Synpotic Soil Characterization"
output: 
  github_document:
  html_preview: true

@@

**Gravimetric moisture**

@@

**Loss on ignition (% organic matter)**

```{r loi}
tar_read(gg_loi)
```

**pH**

@@

**specific conductance**

@@

**total CNS**
```{r tctnts}
tar_read(gg_tctnts)
```

**Water extractable organic C**

@@

**Extractable inorganic N**

Inorganic N was extracted using 2M KCl

@@

**ICP results: base cations**

Extracted using 1M NH4Cl

```{r icp-base cations, fig.height=12, fig.width=7}
tar_read(gg_icp)$gg_base_cations
```

**ICP results: other cations**

Extracted using 1M NH4Cl

```{r icp-other cations, fig.height=9, fig.width=7}
tar_read(gg_icp)$gg_other_cations
```

**ICP results: others**

Extracted using 1M NH4Cl

```{r icp-others, fig.height=4, fig.width=7}
tar_read(gg_icp)$gg_others
```
